Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-04 paper.qmd
Updated the paper

true_model_df <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model.rds")
true_model_df_std <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_std.rds")
wireframe_true_model <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_connections.rds")
training_data_two_curvy_not_std <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_data_without_std.rds")

@@

scaled_two_curvy_data_true_model <- df_model_data_two_curvy |>
  filter(type == "true model") |>
  select(-type)

@@

# Apply the scaling
df_model_data_two_curvy <- bind_rows(data_two_curvy, true_model_two_curvy, df_b_two_curvy2)

>>>>

true_model_df <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_std.rds")
true_model_df_std <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_std.rds")
wireframe_true_model <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_true_model_connections.rds")
training_data_two_curvy_not_std <- read_rds("data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_data_without_std.rds")

@@

@@

# Apply the scaling
df_model_data_two_curvy <- bind_rows(
  data_two_curvy, 
  true_model_two_curvy, 
  df_b_two_curvy2)
